Forecasting future oil production in Norway and the UK: a general improved methodology

### 2014-07-16 Publications/Forecasting  Future Oil Production/Source/manuscript.tex
Latest version.

\maketitle
\begin{abstract}
\noindent We present a new Monte-Carlo methodology to forecast
the crude oil production of Norway and the U.K. based on a two-step process,
(i) the nonlinear extrapolation of the current/past
performances of individual oil fields and (ii) a stochastic model
of the frequency of future oil field discoveries. Compared
with the standard methodology that tends to underestimate remaining oil reserves,
our method gives a better description of future oil production, as validated by
our back-tests starting in 2008. Specifically, we predict remaining reserves
extractable until 2030 to be $188 \pm 10$ million barrels for Norway and $98 \pm10$ million
barrels for the UK, which are respectively $45\%$ and $66\%$ above the
predictions using the standard methodology.
\end{abstract}

@@

\begin{table}[H]
\caption{Remaining oil reserves until 2030 in barrels 
predicted by the extrapolation of the  \textbf{Fit}
of the past country production, and predicted by the Monte-Carlo \textbf{Model}.
The relative difference between these two predictions 
is defined by $\Delta=\frac{\textrm{Model}-\textrm{Fit}}{\textrm{Fit}}$.}
\centering %
\begin{tabular}{lllr}
 & Fit (barrels) & Model (barrels)  & $\Delta$ \tabularnewline
\midrule Norway & $130\cdot10^{6}$  & $188\cdot10^{6}$  & $45\%$\tabularnewline
U.K. & $59\cdot10^{6}$  & $98\cdot10^{6}$  & $66\%$ \tabularnewline
\bottomrule  &  &  & \tabularnewline
\end{tabular}\label{forecast-14}
\end{table}

@@

\begin{table}[H]
\caption{Extrapolation of past oil production (``fit'') and prediction
using the Monte-Carlo model are used on the data set truncated
in 2008. Their forecast for the period 2008-2014 is compared to
the actual realised production.}
\centering %
\begin{tabular}{llll}
 & Actual (barrels) & Fit (barrels) & Model (barrels)\tabularnewline
\midrule Norway & $133\cdot10^{6}$  & $108\cdot10^{6}$  & $130\cdot10^{6}$ \tabularnewline
U.K. & $79\cdot10^{6}$  & $66\cdot10^{6}$  & $75\cdot10^{9}$ \tabularnewline
\bottomrule  &  &  & \tabularnewline
\end{tabular}\label{backtest-08}
\end{table}

@@

\begin{table}[H]
\caption{Remaining oil reserves forecasted for the period 2014-2030 when using
the data truncated in 2008, according to the extrapolation of past oil production (``fit'') and 
the Monte-Carlo model. The relative difference between these two predictions 
is defined by $\Delta=\frac{\textrm{Model}-\textrm{Fit}}{\textrm{Fit}}$.}
\centering %
\begin{tabular}{lllc}
 & Fit (barrels) & Model (barrels) & $\Delta$ \tabularnewline
\midrule Norway 08 & $25\cdot10^{6}$  & $171\cdot10^{6}$  & $-584\%$\tabularnewline
U.K. 08 & $25\cdot10^{6}$  & $91\cdot10^{9}$  & $-264\%$ \tabularnewline
\bottomrule  &  &  & \tabularnewline
\end{tabular}\label{forecast-08}
\end{table}

@@

As shown in table \ref{needs}, at constant consumption, the Monte-Carlo
model predicts that in 2030 the E.U. with Norway will need to increase
its oil imports by $1.3$ million barrels. These imports will most
likely have to come from outside Europe, except for  
non-standard oil sources yet to be developed.

@@

%FIGURE 1
\noindent 
\begin{figure}[H]
\includegraphics[width=1\columnwidth]{oseberg}
\caption{Example of the time evolution of the oil production per day of
a regular field, parameterised beyond the peak in the decay
regime by the stretched exponential 
function (\ref{stretched_exponential}) with $\beta=0.66\pm0.01$ and $\tau=-55\pm1$ months,
shown with the black line.  The one standard deviation given by expression
(\ref{eq:extrapolation}) is represented by the grey band.}
\label{regular} 
\end{figure}

@@

>>>>

\maketitle
\begin{abstract}
\noindent We present a new Monte-Carlo methodology to forecast
the crude oil production of Norway and the U.K. based on a two-step process,
(i) the nonlinear extrapolation of the current/past
performances of individual oil fields and (ii) a stochastic model
of the frequency of future oil field discoveries. Compared
with the standard methodology that tends to underestimate remaining oil reserves,
our method gives a better description of future oil production, as validated by
our back-tests starting in 2008. Specifically, we predict remaining reserves
extractable until 2030 to be $5.7 \pm 0.3$ million barrels for Norway and $3.0 \pm0.3$ billion
barrels for the UK, which are respectively $45\%$ and $66\%$ above the
predictions using the standard methodology.
\end{abstract}

@@

@@

@@

@@

As shown in table \ref{needs}, at constant consumption, the Monte-Carlo
model predicts that in 2030 the E.U. with Norway will need to increase
its daily oil imports by $1.3$ million barrels. These imports will most
likely have to come from outside Europe, except for  
non-standard oil sources yet to be developed.

@@

%FIGURE 1
\noindent 
\begin{figure}[H]
\includegraphics[width=1\columnwidth]{oseberg}
\caption{Example of the time evolution of the oil production per day of
a regular field, parametrised beyond the peak in the decay
regime by the stretched exponential 
function (\ref{stretched_exponential}) with $\beta=0.66\pm0.01$ and $\tau=-55\pm1$ months,
shown with the black line.  The one standard deviation given by expression
(\ref{eq:extrapolation}) is represented by the grey band.}
\label{regular} 
\end{figure}

@@

%TABLE 1

%TABLE 2

\begin{table}[H]
\caption{Remaining oil reserves until 2030 in barrels 
predicted by the extrapolation of the  \textbf{Fit}
of the past country production, and predicted by the Monte-Carlo \textbf{Model}.
The relative difference between these two predictions 
is defined by $\Delta=\frac{\textrm{Model}-\textrm{Fit}}{\textrm{Fit}}$.}
\centering %
\begin{tabular}{lllr}
 & Fit (barrels) & Model (barrels)  & $\Delta$ \tabularnewline
\midrule Norway & $3.95\cdot10^{9}$  & $5.72\cdot10^{9}$  & $45\%$\tabularnewline
U.K. & $1.79\cdot10^{9}$  & $2.98\cdot10^{9}$  & $66\%$ \tabularnewline
\bottomrule  &  &  & \tabularnewline
\end{tabular}\label{forecast-14}
\end{table}

%TABLE 3

\begin{table}[H]
\caption{Extrapolation of past oil production (``fit'') and prediction
using the Monte-Carlo model are used on the data set truncated
in 2008. Their forecast for the period 2008-2014 is compared to
the actual realised production.}
\centering %
\begin{tabular}{llll}
 & Actual (barrels) & Fit (barrels) & Model (barrels)\tabularnewline
\midrule Norway & $4.05\cdot10^{9}$  & $3.28\cdot10^{9}$  & $3.95\cdot10^{9}$ \tabularnewline
U.K. & $2.40\cdot10^{9}$  & $2.00\cdot10^{9}$  & $2.28\cdot10^{9}$ \tabularnewline
\bottomrule  &  &  & \tabularnewline
\end{tabular}\label{backtest-08}
\end{table}

%TABLE 4

\begin{table}[H]
\caption{Remaining oil reserves forecasted for the period 2014-2030 when using
the data truncated in 2008, according to the extrapolation of past oil production (``fit'') and 
the Monte-Carlo model. The relative difference between these two predictions 
is defined by $\Delta=\frac{\textrm{Model}-\textrm{Fit}}{\textrm{Fit}}$.}
\centering %
\begin{tabular}{lllc}
 & Fit (barrels) & Model (barrels) & $\Delta$ \tabularnewline
\midrule Norway 08 & $0.76\cdot10^{9}$  & $5.20\cdot10^{9}$  & $-584\%$\tabularnewline
U.K. 08 & $0.76\cdot10^{9}$  & $2.77\cdot10^{9}$  & $-264\%$ \tabularnewline
\bottomrule  &  &  & \tabularnewline
\end{tabular}\label{forecast-08}
\end{table}

%TABLE 5
